An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2022-06-04 poly-embed-journal/poly-embed-journal.tex
Full pass on appendix E

\section{General characteristics of polyhedra}
\label{app:polyhedra}
\subsection{General definitions for polyhedra}
\label{app:polyhedra:defs}
\begin{definition}[Closed halfspace]
  A closed halfspace is a set of the form $H_{(w,b)}^+ := \{ x \in \reals^d \mid \inprod{x}{w} \geq b\}$ for some $(w,b) \in \reals^d \times \reals$.
  % Similarly let $H_{(w,b)}^- := \{ x \in \reals^d \mid \inprod{x}{w} \leq b\}$.
\end{definition}
\begin{definition}[Hyperplane]
  A hyperplane is a set of the form $H_{(w,b)} := \{ x \in \reals^d \mid \inprod{x}{w} = b\}$ for some $(w,b)\in\reals^d \times \reals$.
  % The halfspaces corresponding to a hyperplane $H = H_{(w,b)}$ are the sets $H_{(w,b)}^+$ and $H_{(w,b)}^-$.
\end{definition} 
Observe that $H_{(w,b)} = \partial H^+_{(w,b)}$, meaning the hyperplane $H_{(w,b)}$ is the boundary of $H^+_{(w,b)}$.
Thus, for any halfspace $H^+$, we have that $H^+$ is one of the two closed halfspaces corresponding to the hyperplane $\partial H^+ = H$.

\begin{definition}[Polyhedron halfspace representation]
	\btw{Def from Ziegler page 28}
	A \emph{polyhedron} $P$ is an intersection of a finite set of closed halfspaces $\H$
  % = \{H^+_i\}_{i=1}^k$
  presented in the form $P = \cap \H$.
\end{definition}
Observe that by the halfspace representation, a polyhedron need not be bounded.

@@

It is often useful to understand polyhedra in terms of their halfspace representations and the set of hyperplanes generating facets of $P$.
To find this set, we must first establish when a halfspace representation is irredundant for a given polyhedron.

\begin{definition}[{\citet{gallier2008notes}}]\label{def:irredundant}
	Let $P = \cap \H$ for a finite set of closed halfspaces $\H$ be a polyhedron.
	We say that $\cap \H$ is an \emph{irredundant decomposition} for $P$ (and $\H$ is irredundant for $P$) if $P$ cannot be expressed as $P = \cap \H'$ for some set of closed halfspaces $\H'$ such that $|\H'| < |\H|$, and redundant otherwise.
	If $\cap \H'$ is an irredundant decomposition of $P$, then we call $\partial H^+$ an irredundant face of $P$ for each $H^+ \in \H'$.
\end{definition}

@@

Given a set $\V \subseteq \reals^d$, we let $\H_{\V} = \{H_v^+ \mid v\in\V\}$ denote the set of halfspaces generated by $\V$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$.
If $\V$ and $\Y$ are understood from context, we may denote $\H := \H_\V \cup\H_\Y$.

For any $S \subseteq \reals^k$, let $\delta(\cdot \mid S):\reals^k \to \reals \cup \{\infty\}$ be the convex indicator function, given by $\delta(x \mid S) = 0$ if $x\in S$ and $\infty$ otherwise.
Throughout, we will work with a function $g_\V$ generated by a set $\V \subseteq \reals^\Y_+$ of the following form.
%Intuitively, one can think of $g_\V$ as a Bayes risk, where $\V$ is the report set, and the input acts like a label distribution.

@@

Using the polyhedral perspective above, we can characterize the hypograph of $\risk L_+ = g_{L(\R)}$ and extract a finite set $\V$ of ``active'' loss vectors, so that $\risk L_+ = g_\V$.
%Let $\H_{L(\R)} = \{H_v^+ \mid v\in L(\R)\}$.
Observe that $L(\R)$ and $\H_{L(\R)}$ may be infinite sets.  
\raft{FYI, I have seen tons of places where you defined things in the text, and then again in the claim/lemma/theorem statement, which actually makes it more confusing.  Probably a hold-over from when you only defined things out of statements}
%We find the existence of a finite $\V \subseteq L(\R)$ such that $g_\V = g_{L(\R)}$, and proceed to work with such a $\V$.
\begin{claim}\label{claim:gV-equals-riskL}
	Suppose we are given a minimizable $L : \R \to \reals^\Y_+$ with polyhedral extended risk $\risk L_+$.
	Then $\hyp(g_{L(\R)}) = \cap(\H_\Y \cup \H_{L(\R)})$.
	Moreover, there is a finite $\V \subseteq L(\R)$ such that $g_{L(\R)} = g_{\V}$. %$\hyp(g_{L(\R)}) = \cap (\H_{\V} \cup \H_\Y) = \hyp(g_{\V})$ and . 
\end{claim}
\begin{proof}
	Observe that $x \in \reals^\Y_+ \iff (x, c) \in \cap \H_\Y$.
	Let $x \in \reals^\Y_+$.
	\begin{align*}
	(x,c) \in \hyp(g_{L(\R)})
	&\iff g_{L(\R)}(x) \geq c & \text{ Definition of hypograph;}\\
	&\iff \risk L_+(x) \geq c & \text{$g_{L(\R)}=\risk L_+$;}\\
	&\iff \inprod{v}{x} \geq c \,\, \forall v \in {L(\R)} & \text{by def of $\risk L_+$ as the infimum over $v \in {L(\R)}$ of}\\
	& & \text{the inner product with $x$ and minimizable;} \\
	&\iff (x,c) \in H^+_{v} \,\, \forall v \in {L(\R)} & \text{by definition of each halfspace;}\\
	&\iff (x,c) \in \cap \H_{L(\R)} & \text{since true for all $v \in {L(\R)}$.}  
	\end{align*}
	Combining the two equalities, we have $\hyp(g_{L(\R)}) = \cap (\H_\Y \cup \H_{L(\R)})$.
	The existence of a finite $\V \subseteq {L(\R)}$ follows as $\risk L_+$ polyhedral implies $\hyp(\risk L_+)$ is a polyhedron, which has a finite representation by definition. \jessiet{Omitting details on why $\V \subseteq {L(\R)}$.}
	%Finally, $\hyp(\risk L_+) = \hyp(g_{L(\R)}) = \hyp(g_{\V})$ if and only if $\risk L_+ = g_{L(\R)} = g_{\V}$. 
\end{proof}

@@

\jessie{We can work with finite $\V$.}
The previous claim allows us to proceed while considering the finite set $\V$ rather than the full range $L(\R)$.
We now evaluate the structure of $g_{L(\R)} = g_\V$ and its hypograph through $\V$.
We will work with any $\V \subseteq \reals^\Y_+$ which is finite.
%Now, we can define $\hyp(g_\V)$ as the intersection of halfspaces generated by $\V$ on the nonnegative orthant.
%\jessie{This isn't reffed anywhere else in the paper.  Remove?}
%\begin{claim}\label{claim:G-intersection-H}
%  Given a finite set $\V \subset \reals^\Y_+$, define $\H = \H_\V \cup \H_\Y$.
%  Then $\hyp(g_\V) = \cap \H$.
%\end{claim}
%\begin{proof}
%  $(x,c) \in \hyp(g_\V) \iff g(x) - c \geq 0 \iff \min_{v \in \V}\inprod{v}{x} - c \geq 0$ and $x \in \reals_+^\Y$, which is true if and only if $\inprod{v}{x} - c \geq 0 \,\forall v \in \V$ and $x_y \geq 0$ for all $y$.
%  In turn, this statement holds if and only if $(x,c) \in H^+_v$ for all $v \in \V$ and in $H^+_y$ for all $y \in \Y$, so $(x,c) \in \cap \H$.
%\end{proof}

\jessie{We want to get to $\V^*$.  We need to build up to it through $\V$ and working with extended BR.}
We proceed with some observations about facets and dimension of $\hyp(g_\V)$ in order to use the \emph{smallest} halfspace representation for $g_{L(\R)} = g_\V$.

@@

With a bit of preliminary work, we can apply Theorem~\ref{thm:polyhedron-uniquely-gen-facets} to observe a unique set of halfspaces $\H^*$ generating $\hyp(g_\V)$.

@@

  Since $\hyp(g_\V)$ is full-dimensional, $\hyp(g_\V) \cap H$ being a facet follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}(i) and (iii).

  To see $\H_\Y \subseteq \H^*$, if there was a $y \in \Y$ such that $H^+_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H^*$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H^*$, or we have a point $x$ such that $x_y < 0$ but $g(x) > -\infty$.
  The first cannot happen as $g_\V$ is concave and finite at $x = e_y \in \reals^\Y_+$.
  The second cannot be true by construction of $g_\V$ since $\V$ is finite including the convex indicator on $\reals^\Y_+$\raft{Couldn't follow this last line, since $\delta$ can be $\infty$}. 
\end{proof}

@@

\begin{corollary}\label{cor:unique-set-loss-vectors-defining-facets}
  Suppose we are given a finite set $\V \subset \reals^\Y_+$, and consider the unique irredundant set $\H^*$ given by Lemma~\ref{lem:G-unique-facets-Hstar}. %such that $\hyp(g_\V) = \cap \H^*$.
  Then

  (i) There is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
  (ii)$F_v$ is a facet of $\hyp(g_\V)$ for each $v\in\V^*$.
  (iii) $\V^* \subseteq \V$.
\end{corollary}
\begin{proof}
%  \raf{Argue that all facets of $G$ are an $H_y \cap G$ or some $H_v \cap G$.  Thus, we can define $\V^*$ by $\H_\Y \cup \H_{\V^*} = \H^*$.  (I.e., $\H^* \setminus \H_\Y = \H_{\V^*}$ for some $\V^*$.)}
%
  (i)Since $\hyp(g_\V)$ is full-dimensional, the facets of $\hyp(g_\V)$ are uniquely determined by the hyperplanes $H$ such that $H = \partial H^+$ and $H^+ \in \H^*$\raft{was ``$\H^* = \{H^+\}$''} by Lemma~\ref{lem:G-unique-facets-Hstar}.
  Any facet must then be some intersection of an $H_y \cap \hyp(g_\V)$ or $H_v \cap \hyp(g_\V)$.
  Consider $\H_{\V^*} := \H^* \setminus \H_{\Y}$, and $\V^*$ the unique set generating $\H_{\V^*}$, since $\H_\Y \subseteq \H^*$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
  (ii) Moreover, $H_v \in \H_{\V^*} \subseteq \H^*$ generates the facet $F_v$ of $\hyp(g_\V)$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
%
%  The moreover follows immediately since $\H_{\V^*} \subseteq \H^*$ and every $H^+ \in \H^*$ defines a facet by Lemma~\ref{lem:G-unique-facets-Hstar}.
  (iii)  $\H_\Y \cup \H_{\V^*} = \H^*$ by Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, and $\H^* \subseteq \H = \H_\Y \cup \H_{\V}$ by Lemma~\ref{lem:G-unique-facets-Hstar}, ergo $\V^* \subseteq \V$.
\end{proof}

@@

\begin{proposition}\label{prop:poly-risk-assumption-satisfied}
	Given a minimizable loss $L : \R \to \reals^\Y_+$ such that $\risk L_+$ is polyhedral, there exists a finite $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
\end{proposition}
\begin{proof}
	\jessie{TODO}
	Given $L$ with polyhedral $\risk L_+$, Claim~\ref{claim:gV-equals-riskL} gives a finite set $\V \subseteq L(\R)$ such that $g_{L(\R)} = g_\V$. 
	Now consider the unique $\V^* \subseteq \V \subseteq L(\R)$ that is given in Corollary~\ref{cor:unique-set-loss-vectors-defining-facets} such that $g_{L(\R)} = g_\V = g_{\V^*}$.
	Equality of the hypographs follows immediately from equailty of the graphs.
	Finally, by construction in Lemma~\ref{lem:G-unique-facets-Hstar}, we additionally have $\H^* = \H_\Y \cup \H_{\V^*}$, and $\cap \H^*$ is irredundant.
%	WTS
%	(i) $\V^* \subseteq L(\R)$ -- done
%	(ii) $\V^*$ unique and smallest
%	(iii) $g_{L(\R)} = g_{\V^*}$
%	(iv) $\hyp(g_{L(\R)}) = \hyp(g_{\V^*}) = \cap (\H_{\V^*} \cup \H_\Y)$
\end{proof}

@@

Given a polyhedron $P$, we denote the face $F^P_v := H_v \cap P$.
If $P$ is understood from context, we simply denote this face $F_v$.
We now define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
The projected faces generated by $\V^*$ cover the nonnegative orthant.

@@

\jessie{Projection $\pi$ preserves dimensions so we can move from extended risk to extended level set and back}
Since we preserve the dimension of these projected spaces, we can now study equivalence of projected faces of the hypograph and regions of support of $g_\V$ for any $v \in L(\R)$.

@@

Taking $L,\V^*$ as in Assumption~\ref{assum:V-star-exists-infinite} and a face of $\hyp(g_{\V^*})$, $F_{v^*} = H_{v^*} \cap \hyp(g_{\V^*})$ for $v^* \in \V^*$, the projection $\pi$ preserves full-dimensionality.
\begin{claim}\label{claim:projected-Vstar-faces-full-dim}
	Given $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, define $F_v := F^{\hyp(g_{\V^*})}_v = H_v \cap \hyp(g_{\V^*})$.
	For all $v \in \V^*$, $\pi(F_v)$ is full dimensional in $\reals_+^\Y$.
	\btw{$\Lambda$ is exactly the set of FDLS; Will lead to $\Theta_{\V^*}$ are exactly the full dimensional level sets over simplex (6).}
\end{claim}
\begin{proof}
	By Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, $F_v$ is a facet of $\hyp(g_{\V^*})$ in $\reals^d_+$, meaning it is $(d - 1)$-dimensional.
	Moreover, Claim~\ref{claim:pi-preserves-dim} states that the dimension of $F_v$ is preserved for each $v \in \V^*$.
	Thus, $\dim(F_v) = \dim(\pi(F_v)) = |\Y|$.
\end{proof}

@@

\begin{claim}\label{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}
	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
	For $\V' \subseteq L(\R)$, we have
	$\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \V^* \subseteq \V'$.\btw{Will get us to REP $\iff$ $\V^* \subseteq L(R')$ (3).}
\end{claim}
\begin{proof}
	\jessiet{Revisit- just rewrote (Mar 10)}
	For any $v \in \V$, define $F_v := F^{\hyp(g_\V)}_v$.
	%We would like to show $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = \hyp(g_\V) := G$, then the result follows by a corollary of the assumption. %apply Corollary~\ref{cor:anything-gen-G-subset-Hstar}.

@@

	($\implies$) 
	For contraposition, suppose $\V^* \not \subseteq \V'$.
	Then $\exists v \in \V^* \setminus \V'$.
	Observe that $\V^*$ is unique and irredundant (by assumption) and $\pi(F_v)$ is full-dimensional in $\reals^\Y_+$ by Claim~\ref{claim:projected-Vstar-faces-full-dim}.
	Moreover, $\pi(F_v) \not \in \cup_{v' \in \V'} \pi(F_v)$, which implies $\cup_{v' \in \V'} \pi(F_v) \neq \cup_{v^* \in \V^*} \pi(F_{v^*}) = \reals^\Y_+$.

@@

We now claim that a set of projected faces $\{F^{\hyp(g_{L(\R)})}_v\}_{v \in \V'}$ for some $\V'$ will cover $\reals^\Y_+$ if and only if $\V^* \subseteq \V'$.
Given a finite set $\V^* \subset \reals^\Y_+$, we denote $\Lambda_{S} := \{\pi(F^{\hyp(g_{L(\R)})}_v) \mid v \in S\}$ as the set of projected facets generated by $S$.

@@

	It then suffices to show that if $F_v := H_v \cap \hyp(g_{\V^*})$ is a face of the facet $F_y := H_y \cap \hyp(g_{\V^*})$ for some $y\in \Y$, then it must also be a face of $F_{v^*}$ for a $v \in \V^*$; it suffices to show $F_v$ is not a facet, and thus $F_v \neq F_y$.
	Recall from the definition of a face that $F_v = \hyp(g_{\V^*}) \cap H_v$ and $F_y = \hyp(g_{\V^*}) \cap H_y$.
	As facets of a polyhedron are (uniquely) determined by hyperplanes and $F_y$ is a facet, then if $F_v$ is a facet we must have $v \in \V^*$, and constructed $\V^*$ such that $\H_{\V^*} \cap \H_\Y = \emptyset$.
	Thus, $F_v \neq F_y$ by unique determination of facets.
	If $F_v$ is not a facet of $\hyp(g_{\V^*})$, then $F_v \neq F_y$ is immediate as $F_y$ is a facet of $\hyp(g_{\V^*})$. 
	In both cases, we have $F_v \neq F_y$, and the result follows.

>>>>

\section{General characteristics of polyhedra}
\label{app:polyhedra}
\subsection{General definitions for polyhedra}
\label{app:polyhedra:defs}
\begin{definition}[Closed halfspace]
  A closed halfspace is a set of the form $H_{(w,b)}^+ := \{ x \in \reals^d \mid \inprod{x}{w} \geq b\}$ for some $(w,b) \in \reals^d \times \reals$.
  % Similarly let $H_{(w,b)}^- := \{ x \in \reals^d \mid \inprod{x}{w} \leq b\}$.
\end{definition}
\begin{definition}[Hyperplane]
  A hyperplane is a set of the form $H_{(w,b)} := \{ x \in \reals^d \mid \inprod{x}{w} = b\}$ for some $(w,b)\in\reals^d \times \reals$.
  % The halfspaces corresponding to a hyperplane $H = H_{(w,b)}$ are the sets $H_{(w,b)}^+$ and $H_{(w,b)}^-$.
\end{definition}

Observe that $H_{(w,b)} = \partial H^+_{(w,b)}$, meaning the hyperplane $H_{(w,b)}$ is the boundary of $H^+_{(w,b)}$.
Thus, for any halfspace $H^+$, we have that $H^+$ is one of the two closed halfspaces corresponding to the hyperplane $\partial H^+ = H$.

\begin{definition}[Polyhedron halfspace representation]
	\btw{Def from Ziegler page 28}
	A \emph{polyhedron} $P$ is an intersection of a finite set of closed halfspaces $\H$
  % = \{H^+_i\}_{i=1}^k$
  presented in the form $P = \cap \H$.
  Here, we say $\H$ is a halfspace representation for $P$.
\end{definition}

\noindent
Observe that by the halfspace representation, a polyhedron need not be bounded.

@@

It is often useful to understand polyhedra in terms of their halfspace representations and the set of hyperplanes generating facets of $P$.
To find this set, we must first establish when a halfspace representation is irredundant for a given polyhedron, as this irredundant set corresponds to the facets of a polyhedron in a natural way.

\begin{definition}[Adapted from {\citet{gallier2008notes}}]\label{def:irredundant}
	Let $P = \cap \H$ for a finite set of closed halfspaces $\H$ be a polyhedron.
	We say that $\cap \H$ is an \emph{irredundant decomposition} for $P$ (and $\H$ is irredundant for $P$) if $P$ cannot be expressed as $P = \cap \H'$ for some set of closed halfspaces $\H'$ such that $|\H'| < |\H|$, and redundant otherwise.
	If $\cap \H'$ is an irredundant decomposition of $P$, then we call $\partial H^+$ an irredundant face of $P$ for each $H^+ \in \H'$.\jessiet{Added this sentence but not sure if it's necessary anymore.}
\end{definition}

@@

Given a set $\V \subseteq \reals^d$, we let $\H_{\V} = \{H_v^+ \mid v\in\V\}$ denote the set of halfspaces generated by $\V$, $\H_\Y = \{H_y^+ \mid y\in\Y\}$.
%If $\V$ and $\Y$ are understood from context, we may denote $\H := \H_\V \cup\H_\Y$.

For any $S \subseteq \reals^k$, let $\delta(\cdot \mid S):\reals^k \to \reals \cup \{\infty\}$ be the convex indicator function, given by $\delta(x \mid S) = 0$ if $x\in S$ and $\infty$ otherwise.
Throughout, we will work with a function $g_\V$ generated by a set $\V \subseteq \reals^\Y_+$ of the following form, often polyhedral (but concave).
%Intuitively, one can think of $g_\V$ as a Bayes risk, where $\V$ is the report set, and the input acts like a label distribution.

@@

Using the polyhedral perspective above, we can characterize the hypograph of $\risk L_+ = g_{L(\R)}$ and extract a \emph{finite} set $\V$ of ``active'' loss vectors, so that $\risk L_+ = g_\V$.
%Let $\H_{L(\R)} = \{H_v^+ \mid v\in L(\R)\}$.
Observe that $L(\R)$ and $\H_{L(\R)}$ may be infinite sets.  
\raft{FYI, I have seen tons of places where you defined things in the text, and then again in the claim/lemma/theorem statement, which actually makes it more confusing.  Probably a hold-over from when you only defined things out of statements}
%We find the existence of a finite $\V \subseteq L(\R)$ such that $g_\V = g_{L(\R)}$, and proceed to work with such a $\V$.
\begin{claim}\label{claim:gV-equals-riskL}
	Suppose we are given a minimizable $L : \R \to \reals^\Y_+$ with polyhedral extended risk $\risk L_+$.
	Then $\hyp(g_{L(\R)}) = \cap(\H_\Y \cup \H_{L(\R)})$.
	Moreover, there is a finite $\V \subseteq L(\R)$ such that $g_{L(\R)} = g_{\V}$. %$\hyp(g_{L(\R)}) = \cap (\H_{\V} \cup \H_\Y) = \hyp(g_{\V})$ and . 
\end{claim}
\begin{proof}
	Observe that $x \in \reals^\Y_+ \iff (x, c) \in \cap \H_\Y$.
	Let $x \in \reals^\Y_+$.
	\begin{align*}
	(x,c) \in \hyp(g_{L(\R)})
	&\iff g_{L(\R)}(x) \geq c & \text{ Definition of hypograph;}\\
	&\iff \risk L_+(x) \geq c & \text{$g_{L(\R)}=\risk L_+$;}\\
	&\iff \inprod{v}{x} \geq c \,\, \forall v \in {L(\R)} & \text{by def of $\risk L_+$ as the infimum over $v \in {L(\R)}$ of}\\
	& & \text{the inner product with $x$ and minimizable;} \\
	&\iff (x,c) \in H^+_{v} \,\, \forall v \in {L(\R)} & \text{by definition of each halfspace;}\\
	&\iff (x,c) \in \cap \H_{L(\R)} & \text{since true for all $v \in {L(\R)}$.}  
	\end{align*}
	Combining the two equalities, we have $\hyp(g_{L(\R)}) = \cap (\H_\Y \cup \H_{L(\R)})$.
	The existence of a finite $\V \subseteq {L(\R)}$ follows as $\risk L_+$ polyhedral implies $\hyp(\risk L_+)$ is a polyhedron, which has a finite representation by definition. \jessiet{Omitting details on why $\V \subseteq {L(\R)}$.}
	%Finally, $\hyp(\risk L_+) = \hyp(g_{L(\R)}) = \hyp(g_{\V})$ if and only if $\risk L_+ = g_{L(\R)} = g_{\V}$. 
\end{proof}

@@

The previous claim allows us to proceed while considering the finite set $\V$ rather than the full range $L(\R)$.
We now evaluate the structure of $g_{L(\R)} = g_\V$ and its hypograph through $\V$.
%We will work with any $\V \subseteq \reals^\Y_+$ which is finite.
%Now, we can define $\hyp(g_\V)$ as the intersection of halfspaces generated by $\V$ on the nonnegative orthant.
%\jessie{This isn't reffed anywhere else in the paper.  Remove?}
%\begin{claim}\label{claim:G-intersection-H}
%  Given a finite set $\V \subset \reals^\Y_+$, define $\H = \H_\V \cup \H_\Y$.
%  Then $\hyp(g_\V) = \cap \H$.
%\end{claim}
%\begin{proof}
%  $(x,c) \in \hyp(g_\V) \iff g(x) - c \geq 0 \iff \min_{v \in \V}\inprod{v}{x} - c \geq 0$ and $x \in \reals_+^\Y$, which is true if and only if $\inprod{v}{x} - c \geq 0 \,\forall v \in \V$ and $x_y \geq 0$ for all $y$.
%  In turn, this statement holds if and only if $(x,c) \in H^+_v$ for all $v \in \V$ and in $H^+_y$ for all $y \in \Y$, so $(x,c) \in \cap \H$.
%\end{proof}

\jessie{We want to get to $\V^*$.  We need to build up to it through $\V$ and working with extended BR.}
We proceed with some observations about facets and dimension of $\hyp(g_\V)$ in order to use the \emph{smallest} halfspace representation $\H^*$ for $g_{L(\R)} = g_\V$.

@@

With a bit of preliminary work, we can apply Theorem~\ref{thm:polyhedron-uniquely-gen-facets} to observe a unique irredundant halfspace representation $\H^*$ generating $\hyp(g_\V)$.

@@

  Since $\hyp(g_\V)$ is full-dimensional, $\hyp(g_\V) \cap H$ being a facet follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}(ii) and (iii).

  To see $\H_\Y \subseteq \H^*$, if there was a $y \in \Y$ such that $H^+_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H^*$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H^*$, or we have a point $x$ such that $x_y < 0$ but $g(x) > -\infty$.
  The first cannot happen as $g_\V$ is concave and finite at $x = e_y \in \reals^\Y_+$.
  The second cannot be true by construction of $g_\V$ since $\V$ is finite including the convex indicator on $\reals^\Y_+$\raft{Couldn't follow this last line, since $\delta$ can be $\infty$\jessie{does it help that it's minus the convex indicator?}}. 
\end{proof}

@@

\begin{corollary}\label{cor:unique-set-loss-vectors-defining-facets}
  Suppose we are given a finite set $\V \subset \reals^\Y_+$, and consider the unique irredundant set $\H^*$ given by Lemma~\ref{lem:G-unique-facets-Hstar}. %such that $\hyp(g_\V) = \cap \H^*$.
  Then
  (i) There is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
  (ii)$F_v$ is a facet of $\hyp(g_\V)$ for each $v\in\V^*$.
  (iii) $\V^* \subseteq \V$.
\end{corollary}
\begin{proof}
%  \raf{Argue that all facets of $G$ are an $H_y \cap G$ or some $H_v \cap G$.  Thus, we can define $\V^*$ by $\H_\Y \cup \H_{\V^*} = \H^*$.  (I.e., $\H^* \setminus \H_\Y = \H_{\V^*}$ for some $\V^*$.)}
%
  (i) Since $\hyp(g_\V)$ is full-dimensional, the facets of $\hyp(g_\V)$ are uniquely determined by the hyperplanes $H$ such that $H = \partial H^+$ and $H^+ \in \H^*$\raft{was ``$\H^* = \{H^+\}$''} by Lemma~\ref{lem:G-unique-facets-Hstar}.
  Any facet must then be some intersection of an $H_y \cap \hyp(g_\V)$ or $H_v \cap \hyp(g_\V)$.
  Since $\H_\Y \subseteq \H^*$ by Lemma~\ref{lem:G-unique-facets-Hstar}, take $\H_{\V^*} := \H^* \setminus \H_{\Y}$, and $\V^*$ the unique set generating $\H_{\V^*}$.
  (ii) Moreover, $H_v \in \H_{\V^*} \subseteq \H^*$ generates the facet $F_v$ of $\hyp(g_\V)$ by Lemma~\ref{lem:G-unique-facets-Hstar}.
%
%  The moreover follows immediately since $\H_{\V^*} \subseteq \H^*$ and every $H^+ \in \H^*$ defines a facet by Lemma~\ref{lem:G-unique-facets-Hstar}.
  (iii)  $\H_\Y \cup \H_{\V^*} = \H^*$ by (i), and $\H^* \subseteq \H = \H_\Y \cup \H_{\V}$ by Lemma~\ref{lem:G-unique-facets-Hstar}, ergo $\V^* \subseteq \V$.
\end{proof}

@@

\begin{proposition}\label{prop:poly-risk-assumption-satisfied}
	Given a minimizable loss $L : \R \to \reals^\Y_+$ such that $\risk L_+$ is polyhedral, there exists a finite $\V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
\end{proposition}
\begin{proof}
	\jessie{Can use careful eyes}
	Given $L$ with polyhedral $\risk L_+$, Claim~\ref{claim:gV-equals-riskL} gives a finite set $\V \subseteq L(\R)$ such that $g_{L(\R)} = g_\V$. 
	Now consider the unique $\V^* \subseteq \V \subseteq L(\R)$ that is given in Corollary~\ref{cor:unique-set-loss-vectors-defining-facets} such that $g_{L(\R)} = g_\V = g_{\V^*}$.
	Equality of the hypographs follows immediately from equailty of the graphs.
	Finally, by construction in Lemma~\ref{lem:G-unique-facets-Hstar}, we additionally have $\H^* = \H_\Y \cup \H_{\V^*}$, and $\cap \H^*$ is irredundant.
%	WTS
%	(i) $\V^* \subseteq L(\R)$ -- done
%	(ii) $\V^*$ unique and smallest
%	(iii) $g_{L(\R)} = g_{\V^*}$
%	(iv) $\hyp(g_{L(\R)}) = \hyp(g_{\V^*}) = \cap (\H_{\V^*} \cup \H_\Y)$
\end{proof}

@@

Given a polyhedron $P$, we denote the face $F^P_v := H_v \cap P$.
If $P$ is understood from context, we simply denote this face $F_v$.
We now define the projection $\pi:\reals^\Y\times \reals \to \reals^\Y, (x,c) \mapsto x$.
%The projected faces generated by $\V^*$ cover the nonnegative orthant.

@@

Since we preserve the dimension of these projected spaces, we can now study equivalence of projected faces of the hypograph and regions of support of $g_{\V^*}$ for any $v \in L(\R)$.

@@

%Taking $L,\V^*$ as in Assumption~\ref{assum:V-star-exists-infinite} and a face of $\hyp(g_{\V^*})$, $F_{v^*} = H_{v^*} \cap \hyp(g_{\V^*})$ for $v^* \in \V^*$, the projection $\pi$ preserves full-dimensionality.
\begin{claim}\label{claim:projected-Vstar-faces-full-dim}
	Given $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}, define $F_v := F^{\hyp(g_{\V^*})}_v = H_v \cap \hyp(g_{\V^*})$.
	For all $v \in \V^*$, $\pi(F_v)$ is full dimensional in $\reals_+^\Y$.
	\btw{$\Lambda$ is exactly the set of FDLS; Will lead to $\Theta_{\V^*}$ are exactly the full dimensional level sets over simplex (6).}
\end{claim}
\begin{proof}
	By Corollary~\ref{cor:unique-set-loss-vectors-defining-facets}, $F_v$ is a facet of $\hyp(g_{\V^*})$ in $\reals^d_+$, meaning it is $(d - 1)$-dimensional.
	Moreover, Claim~\ref{claim:pi-preserves-dim} states that the dimension of $F_v$ is preserved for each $v \in \V^*$.
	Thus, $d-1 = |\Y| = \dim(F_v) = \dim(\pi(F_v))$.
\end{proof}

@@

\begin{claim}\label{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}
	Consider $L, \V^*$ satisfying Assumption~\ref{assum:V-star-exists-infinite}.
	For $\V' \subseteq L(\R)$, we have
	$\cup_{v\in\V'} \pi(F^{\hyp(g_{\V^*})}_v) = \reals^\Y_+ \iff \V^* \subseteq \V'$.\btw{Will get us to REP $\iff$ $\V^* \subseteq L(R')$ (3).}
\end{claim}
\begin{proof}
	\jessiet{Revisit- just rewrote (Mar 10)}
	For any $v \in \V$, define $F_v := F^{\hyp(g_{\V^*})}_v$.
	%We would like to show $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = \hyp(g_\V) := G$, then the result follows by a corollary of the assumption. %apply Corollary~\ref{cor:anything-gen-G-subset-Hstar}.

@@

	($\implies$) 
	For contraposition, suppose $\V^* \not \subseteq \V'$.
	Then $\exists v \in \V^* \setminus \V'$.
	Observe that $\V^*$ is unique, $\H^*$ is irredundant by assumption, and $\pi(F_v)$ is full-dimensional in $\reals^\Y_+$ by Claim~\ref{claim:projected-Vstar-faces-full-dim}.
	Moreover, $\pi(F_v) \not \in \cup_{v' \in \V'} \pi(F_v)$, which implies $\cup_{v' \in \V'} \pi(F_v) \neq \cup_{v^* \in \V^*} \pi(F_{v^*}) = \reals^\Y_+$.

@@

We now claim that a set of projected faces $\{F^{\hyp(g_{L(\R)})}_v\}_{v \in \V'}$ \jessiet{Diff between $\{F^{\hyp(g_{L(\R)})}_v\}_{v \in \V'}$ and $\{F^{\hyp(g_{\V^*})}_v\}_{v \in \V'}$?}for some $\V'$ will cover $\reals^\Y_+$ if and only if $\V^* \subseteq \V'$.
Given a finite set $\V^* \subset \reals^\Y_+$, we denote $\Lambda_{S} := \{\pi(F^{\hyp(g_{L(\R)})}_v) \mid v \in S\}$ as the set of projected facets generated by $S$.

@@

	It then suffices to show, for $v \in L(\R)$ that if $F_v := H_v \cap \hyp(g_{\V^*})$ is a face of the facet $F_y := H_y \cap \hyp(g_{\V^*})$ for some $y\in \Y$, then it must also be a face of $F_{v^*}$ for a $v^* \in \V^*$; it suffices to show $F_v$ is not a facet, and thus $F_v \neq F_y$.
	Recall from the definition of a face that $F_v = \hyp(g_{\V^*}) \cap H_v$ and $F_y = \hyp(g_{\V^*}) \cap H_y$.
	As facets of a polyhedron are (uniquely) determined by hyperplanes and $F_y$ is a facet, then if $F_v$ is a facet we must have $v \in \V^*$, and $\V^*$ is constructed so that $\H_{\V^*} \cap \H_\Y = \emptyset$.
	Thus, $F_v \neq F_y$ by unique determination of facets.
	If $F_v$ is not a facet of $\hyp(g_{\V^*})$, then $F_v \neq F_y$ is immediate as $F_y$ is a facet of $\hyp(g_{\V^*})$. 
	In both cases, we have $F_v \neq F_y$, and the result follows.
